Measuring individual differences in the understanding of gaze cues across the lifespan

### 2022-03-21 paper/manuscript.Rmd
minor clean up

# -- POSSIBLE ROUGH STRUCTURE -- 
# intro
## individual differences in dev psy
- reliable tasks: need variation, more trials

## exisiting tasks for social cognition
- wellman

## current goal
- standardized, easy to use, continuous

# methods (let's see whether we want this generic heading...)
## design of our task
- training trials (touch & fam together, click on visible balloon / visible target flight, voice over trials)
- test trials
- flexible: two versions, can also use discrete
- face value

- stimulus timing

## implementation / development
- JS, HTML, CSS
- parcel?!
- SVG: scalable
- webapp: portable across devices, flexible, no hard system requirements
- response collection: file format, variables saved (click responses)

## data processing
- workflow for collecting data
- pipeline? downloading server data into r, coverting coordinate systems

# does our task induce variation?
## participants: kiga & prolific vali
## procedure 
## results
- for hedge & box
- sanity check: developmental trajectory
- remote testing: online child sample as side note

# do we capture variation reliably?
## participants: relikiga & prolific reli
## results: 
- internal consistency?
- test-retest

# exploratory: external validity
## participants: subsample kiga & relikiga with questionnaire data
## results: 
- peer exposure (box & hedge combined?)

# discussion
## limitations
## future development / extending the task
# conclusion

\newpage
# Introduction 
Idea for an opener :)

@@

- individual differences in developmental psychology
- reliable tasks, variation needed, more trials
- existing tasks for social cognition: wellman
- goal of the current project

# Design of our balloon finding task

@@

The web-app was programmed in JavaScript (ECMAScript 2015, i.e., ES6), HTML5, CSS and PHP. 
For the web-app development, we chose the zero configuration bundler Parcel. It enables a live server for debugging, makes imports easy, and minifies scripts in order to save data storage.
For the design of the landing pages, the CSS library Material Components Web (TODO: insert citation) was used. 
For stimulus presentation, a scalable vector graphic (SVG) composition was parsed. This way, the composition scales according to the user's view port without loss of quality, while keeping the aspect ratio and relative object positions constant. 
Furthermore, SVGs allow us to define all composite parts of the scene (e.g., pupil of the agent) individually. This is needed for precisely calculating exact pupil and target locations and sizes. Additionally, it makes it easy to adjust the stimuli and, for example, add another agent to the scene.
The GreenSock Animation Platform (GSAP; TODO: insert citation) library was used to animate the movement of single SVG elements. 
We use URL parameters to capture the participant's ID, language and study version.

@@

## Results
- sanity check: developmental trajectory

### Interindividual variation
We captured a developmental trajectory of gaze cue understanding. With increasing age, participants get more and more accurate in their performance.

(ref:figlab2) **Measuring interindividual variation**. 
(a) Developmental trajectory in continuous *hedge* version. Performance is measured as average imprecision, i.e., the absolute distance between the target's center and the participant's click. The unit of imprecision is counted in the width of the target, i.e., a participant with an imprecision of 1 clicked in average one target width to the left or right of the true target center. 
(b) Internal consistency (odd-even split) in hedge child sample. (c) Internal consistency in hedge adult sample. (d) Test-retest reliability in hedge child sample. (e) Test-retest reliability in hedge adult sample.
(f) Developmental trajectory in discrete *box* version. Performance is measured as the proportion of correct responses, i.e., how many times the participant clicked on the box that actually contained the target. Dotted black line shows level of performance expected by chance (for child sample 20%, i.e., 1 out of 5 boxes; for adult sample 12.5%, i.e., 1 out of 8 boxes).
(g) Internal consistency (odd-even split) in box child sample. (h) Internal consistency in box adult sample. (i) Test-retest reliability in box child sample. (j) Test-retest reliability in box adult sample.
Regression lines with 95% CI show product-moment-correlations with Pearson's correlation coefficient r. 
Large data points with 95% CI (based on non-parametric bootstrap) represent performance means by age group (binned by year). 
Small data points show the mean performance for each subject. Shape of data points represents data collection mode: opaque round circles with stand for in-person supervised data collection, translucent diamonds stand for remote unsupervised data collection. Color of data points represent each age group (binned by year).

@@

### Internal consistency
```{r variation_splithalf}
splithalf <- readRDS(file = "../stats/gafo-splithalf.rds") 
```

TODO: cite splithalfr package
We were interested to see whether our found inter-individual variation in gaze cue understanding is reliable. As a first step, we investigated the internal consistency. In the hedge version, we found a splithalf reliability of 
`r splithalf$hedge_odd_even` (95%CI [`r splithalf$hedge_odd_even_ci_lower`;`r splithalf$hedge_odd_even_ci_upper`]) when applying an odd-even split, and splithalf reliability of 
`r splithalf$hedge_first_second` (95%CI [`r splithalf$hedge_first_second_ci_lower`;`r splithalf$hedge_first_second_ci_upper`]) when splitting trials in the first and second test halves. 
For the box version, we found a splithalf reliability of 
`r splithalf$box_odd_even` (95%CI [`r splithalf$box_odd_even_ci_lower`;`r splithalf$box_odd_even_ci_upper`]) when applying an odd-even split, and splithalf reliability of 
`r splithalf$box_first_second` (95%CI [`r splithalf$box_first_second_ci_lower`;`r splithalf$box_first_second_ci_upper`]) when splitting trials in the first and second test halves.

@@

As Figure 5 shows, our remotely collected data closely resembled the data from the kindergarten sample. We found a minor difference in that children that participate remotely are slightly more precise. This difference was mainly driven by the younger participants and especially prominent in the box version of the task. It is conceivable that caregivers were especially prone to help with the behavior of younger children. In the box version, caregivers might have had more opportunities to interfere since they carried out the clicking for their children.

(ref:figlab5) **Comparing data collection modes**. 
The regression line shows the developmental trajectory (with 95% CI) of children's performance by age, separated by data collection mode. 
Colored diamonds show means by age in years (with 95% CI based on non-parametric bootstrap). Light shapes show the mean performance for each subject.
(a) Variation in the hedge version split by data collection mode. Performance is measured as the average imprecision, i.e., the absolute click distance between the target's center and the participant's click. The unit of imprecision is counted in the width of the target, i.e., a participant with an imprecision of 1 clicked in average one target width to the left or right of the true target center. 
(b) Variation in the box version split by data collection mode. Performance is measured as the proportion of correct responses, i.e., how many times the participant clicked on the box that actually contained the target. The straight line shows level of performance expected by chance for the child sample (20%, i.e., 1 out of 5 boxes).

## Discussion
Study 1 showed that our newly implemented balloon finding task can be used to study gaze cue understanding in both children and adults. With increasing age, participants got more and more precise in locating the target. We found inter-individual variation in across all age groups: some three-year-olds were more precise than some five-year-olds. Internal consistency indicated that the measured variation was systematic. These results hold for both the continuous hedge version as well as the discrete box version of the task. Furthermore, we found a comparable developmental trajectory for an unsupervised remote child sample. This underlines how flexibly our new task can be used.

# Can we capture variation reliably?
Based on the results of Study 1, we wanted to further investigate whether the variation that we captured with our balloon finding task is reliable. For this aim, we assessed the test-retest reliability by testing the same individual twice. The pre-registrations can be found here: https://osf.io/xqm73 (child sample) and here: https://osf.io/nu62m (adult sample). Participants were equally distributed across the two study versions. The study was approved by an internal ethics committee at the Max Planck Institute for Evolutionary Anthropology. Data was collected between XXX 2021 and XXX 2022.

@@

>>>>

# Introduction 
Idea for an opener :)

@@

- individual differences in developmental psychology:
- reliable tasks, variation needed, more trials
- existing tasks for social cognition: wellman
- goal of the current project: standardized, easy to use continuous methods

# Design of our balloon finding task
- face value of task (or maybe in intro already?)

@@

The web-app was programmed in JavaScript (ECMAScript 2015, i.e., ES6), HTML5, CSS and PHP. 
We utilized the zero configuration bundler Parcel to enable a live server for debugging, easy imports and minified scripts in order to save data storage.
For stimulus presentation, a scalable vector graphic (SVG) composition was parsed. This way, the composition scales according to the user's view port without loss of quality, while keeping the aspect ratio and relative object positions constant. 
Furthermore, SVGs allow us to define all composite parts of the scene (e.g., pupil of the agent) individually. This is needed for precisely calculating exact pupil and target locations and sizes. Additionally, it makes it easy to adjust the stimuli and, for example, add another agent to the scene.
The GreenSock Animation Platform (GSAP; TODO: insert citation) library was used to animate the movement of single SVG elements. 
We use URL parameters to capture the participant's ID, language and study version.

@@

## Results
(ref:figlab2) **Measuring interindividual variation**. 
(a) Developmental trajectory in continuous *hedge* version. Performance is measured as average imprecision, i.e., the absolute distance between the target's center and the participant's click. The unit of imprecision is counted in the width of the target, i.e., a participant with an imprecision of 1 clicked in average one target width to the left or right of the true target center. 
(b) Internal consistency (odd-even split) in hedge child sample. (c) Internal consistency in hedge adult sample. (d) Test-retest reliability in hedge child sample. (e) Test-retest reliability in hedge adult sample.
(f) Developmental trajectory in discrete *box* version. Performance is measured as the proportion of correct responses, i.e., how many times the participant clicked on the box that actually contained the target. Dotted black line shows level of performance expected by chance (for child sample 20%, i.e., 1 out of 5 boxes; for adult sample 12.5%, i.e., 1 out of 8 boxes).
(g) Internal consistency (odd-even split) in box child sample. (h) Internal consistency in box adult sample. (i) Test-retest reliability in box child sample. (j) Test-retest reliability in box adult sample.
Regression lines with 95% CI show product-moment-correlations with Pearson's correlation coefficient r. 
Large data points with 95% CI (based on non-parametric bootstrap) represent performance means by age group (binned by year). 
Small data points show the mean performance for each subject. Shape of data points represents data collection mode: opaque round circles with stand for in-person supervised data collection, translucent diamonds stand for remote unsupervised data collection. Color of data points represent each age group (binned by year).

@@

We captured a developmental trajectory of gaze cue understanding: with increasing age, participants get more and more accurate in their performance. In the hedge version, children's click imprecision drops with age, while in the box version the proportion of correct responses increases (see Figure 2 A and F). By the end of their sixth year of life, children come close to the adult's proficiency level. We find interindividual variation across studyversions and age groups: some three-year-olds are more accurate in their responses than some five-year-olds.

@@

As Figure 2 A and F show, our remotely collected data closely resembled the data from the kindergarten sample. We found a minor difference in that children that participate remotely are slightly more precise. This difference was mainly driven by the younger participants and especially prominent in the box version of the task. It is conceivable that caregivers were especially prone to help with the behavior of younger children. In the box version, caregivers might have had more opportunities to interfere since they carried out the clicking for their children.

## Discussion
Study 1 showed that our newly implemented balloon finding task can be used to study gaze cue understanding in both children and adults. With increasing age, participants got more and more precise in locating the target. We found inter-individual variation in across all age groups. Furthermore, we found a comparable developmental trajectory for an unsupervised remote child sample. This underlines how flexibly our new task can be used.

# Can we capture variation reliably?
Based on the results of Study 1, we wanted to further investigate whether the variation that we captured with our balloon finding task is reliable. For this aim, we assessed the internal consistency and test-retest reliability. The pre-registrations can be found here: https://osf.io/xqm73 (child sample) and here: https://osf.io/nu62m (adult sample). Participants were equally distributed across the two study versions. The study was approved by an internal ethics committee at the Max Planck Institute for Evolutionary Anthropology. Data was collected between XXX 2021 and XXX 2022.

@@

```{r splithalf}
splithalf <- readRDS(file = "../stats/gafo-splithalf.rds")
```

For estimating the internal consistency, we analyzed the raw performance per subject of the first test day. 
Our main analysis focuses on an odd-even split on our data.  
In the hedge version, odd-even splitting yielded an estimate of `r splithalf$mean[splithalf$studyversion == "hedge" & splithalf$sample == "kids" & splithalf$split == "odd even" & splithalf$stratification == "none"]` for the child sample (see Figure 2B), and an estimate of `r splithalf$mean[splithalf$studyversion == "hedge" & splithalf$sample == "adults" & splithalf$split == "odd even" & splithalf$stratification == "none"]` for the adult sample (see Figure 2C). 
In the box version, odd-even splitting yielded an estimate of `r splithalf$mean[splithalf$studyversion == "box" & splithalf$sample == "kids" & splithalf$split == "odd even" & splithalf$stratification == "none"]` for the child sample (see Figure 2G), and an estimate of `r splithalf$mean[splithalf$studyversion == "box" & splithalf$sample == "adults" & splithalf$split == "odd even" & splithalf$stratification == "none"]` for the adult sample (see Figure 2H).

A recent paper by [TODO: insert citation splithalfr paper] presents new techniques to analyze internal consistency. 
The modern statistical approach of stratification allows for a better representation of the data and experimental structure. 
To compare our traditional approach of a simple odd-even split, we explored the results of random, odd-even and first-second-testhalf splits without and with stratification by target position. As can be seen in Table 1, stratifying by target position leads to similar or even higher estimates. 
As might be expected, we found higher coefficients for the samples with higher variation, i.e. for our continuous hedge version of the task.

```{r}
knitr::kable(splithalf, col.names = c("study version", "age group", "splitting method", "stratification", "mean estimate", "lower 95%CI", "upper 95%CI"))
```

Our results indicated that the measured variation was systematic. These results hold for both the continuous hedge version as well as the discrete box version of the task.

## Discussion

### 2022-03-21 paper/manuscript.tex
minor clean up

\hypertarget{possible-rough-structure}{%
\section{-- POSSIBLE ROUGH STRUCTURE --}\label{possible-rough-structure}}

\hypertarget{intro}{%
\section{intro}\label{intro}}

\hypertarget{individual-differences-in-dev-psy}{%
\subsection{individual differences in dev psy}\label{individual-differences-in-dev-psy}}

\begin{itemize}
\tightlist
\item
  reliable tasks: need variation, more trials
\end{itemize}

\hypertarget{exisiting-tasks-for-social-cognition}{%
\subsection{exisiting tasks for social cognition}\label{exisiting-tasks-for-social-cognition}}

\begin{itemize}
\tightlist
\item
  wellman
\end{itemize}

\hypertarget{current-goal}{%
\subsection{current goal}\label{current-goal}}

\begin{itemize}
\tightlist
\item
  standardized, easy to use, continuous
\end{itemize}

\hypertarget{methods-lets-see-whether-we-want-this-generic-heading}{%
\section{methods (let's see whether we want this generic heading\ldots)}\label{methods-lets-see-whether-we-want-this-generic-heading}}

\hypertarget{design-of-our-task}{%
\subsection{design of our task}\label{design-of-our-task}}

\begin{itemize}
\item
  training trials (touch \& fam together, click on visible balloon / visible target flight, voice over trials)
\item
  test trials
\item
  flexible: two versions, can also use discrete
\item
  face value
\item
  stimulus timing
\end{itemize}

\hypertarget{implementation-development}{%
\subsection{implementation / development}\label{implementation-development}}

\begin{itemize}
\tightlist
\item
  JS, HTML, CSS
\item
  parcel?!
\item
  SVG: scalable
\item
  webapp: portable across devices, flexible, no hard system requirements
\item
  response collection: file format, variables saved (click responses)
\end{itemize}

\hypertarget{data-processing}{%
\subsection{data processing}\label{data-processing}}

\begin{itemize}
\tightlist
\item
  workflow for collecting data
\item
  pipeline? downloading server data into r, coverting coordinate systems
\end{itemize}

\hypertarget{does-our-task-induce-variation}{%
\section{does our task induce variation?}\label{does-our-task-induce-variation}}

\hypertarget{participants-kiga-prolific-vali}{%
\subsection{participants: kiga \& prolific vali}\label{participants-kiga-prolific-vali}}

\hypertarget{procedure}{%
\subsection{procedure}\label{procedure}}

\hypertarget{results}{%
\subsection{results}\label{results}}

\begin{itemize}
\tightlist
\item
  for hedge \& box
\item
  sanity check: developmental trajectory
\item
  remote testing: online child sample as side note
\end{itemize}

\hypertarget{do-we-capture-variation-reliably}{%
\section{do we capture variation reliably?}\label{do-we-capture-variation-reliably}}

\hypertarget{participants-relikiga-prolific-reli}{%
\subsection{participants: relikiga \& prolific reli}\label{participants-relikiga-prolific-reli}}

\hypertarget{results-1}{%
\subsection{results:}\label{results-1}}

\begin{itemize}
\tightlist
\item
  internal consistency?
\item
  test-retest
\end{itemize}

\hypertarget{exploratory-external-validity}{%
\section{exploratory: external validity}\label{exploratory-external-validity}}

\hypertarget{participants-subsample-kiga-relikiga-with-questionnaire-data}{%
\subsection{participants: subsample kiga \& relikiga with questionnaire data}\label{participants-subsample-kiga-relikiga-with-questionnaire-data}}

\hypertarget{results-2}{%
\subsection{results:}\label{results-2}}

\begin{itemize}
\tightlist
\item
  peer exposure (box \& hedge combined?)
\end{itemize}

\hypertarget{discussion}{%
\section{discussion}\label{discussion}}

\hypertarget{limitations}{%
\subsection{limitations}\label{limitations}}

\hypertarget{future-development-extending-the-task}{%
\subsection{future development / extending the task}\label{future-development-extending-the-task}}

\hypertarget{conclusion}{%
\section{conclusion}\label{conclusion}}

@@

\begin{itemize}
\tightlist
\item
  individual differences in developmental psychology
\item
  reliable tasks, variation needed, more trials
\item
  existing tasks for social cognition: wellman
\item
  goal of the current project
\end{itemize}

@@

@@

\hypertarget{data-processing-1}{%
\subsection{Data processing}\label{data-processing-1}}

@@

@@

\hypertarget{results-3}{%
\subsection{Results}\label{results-3}}

\begin{itemize}
\tightlist
\item
  sanity check: developmental trajectory
\end{itemize}

\hypertarget{interindividual-variation}{%
\subsubsection{Interindividual variation}\label{interindividual-variation}}

We captured a developmental trajectory of gaze cue understanding. With increasing age, participants get more and more accurate in their performance.

@@

\hypertarget{internal-consistency}{%
\subsubsection{Internal consistency}\label{internal-consistency}}

TODO: cite splithalfr package
We were interested to see whether our found inter-individual variation in gaze cue understanding is reliable. As a first step, we investigated the internal consistency. In the hedge version, we found a splithalf reliability of
0.72 (95\%CI {[}0.60;0.82{]}) when applying an odd-even split, and splithalf reliability of
0.71 (95\%CI {[}0.51;0.81{]}) when splitting trials in the first and second test halves.
For the box version, we found a splithalf reliability of
0.55 (95\%CI {[}0.35;0.69{]}) when applying an odd-even split, and splithalf reliability of
0.79 (95\%CI {[}0.64;0.86{]}) when splitting trials in the first and second test halves.

@@

As Figure 5 shows, our remotely collected data closely resembled the data from the kindergarten sample. We found a minor difference in that children that participate remotely are slightly more precise. This difference was mainly driven by the younger participants and especially prominent in the box version of the task. It is conceivable that caregivers were especially prone to help with the behavior of younger children. In the box version, caregivers might have had more opportunities to interfere since they carried out the clicking for their children.

Study 1 showed that our newly implemented balloon finding task can be used to study gaze cue understanding in both children and adults. With increasing age, participants got more and more precise in locating the target. We found inter-individual variation in across all age groups: some three-year-olds were more precise than some five-year-olds. Internal consistency indicated that the measured variation was systematic. These results hold for both the continuous hedge version as well as the discrete box version of the task. Furthermore, we found a comparable developmental trajectory for an unsupervised remote child sample. This underlines how flexibly our new task can be used.

@@

Based on the results of Study 1, we wanted to further investigate whether the variation that we captured with our balloon finding task is reliable. For this aim, we assessed the test-retest reliability by testing the same individual twice. The pre-registrations can be found here: \url{https://osf.io/xqm73} (child sample) and here: \url{https://osf.io/nu62m} (adult sample). Participants were equally distributed across the two study versions. The study was approved by an internal ethics committee at the Max Planck Institute for Evolutionary Anthropology. Data was collected between XXX 2021 and XXX 2022.

@@

\hypertarget{results-4}{%
\subsection{Results}\label{results-4}}

@@

@@

\hypertarget{procedure-3}{%
\subsection{Procedure}\label{procedure-3}}

@@

\hypertarget{results-5}{%
\subsection{Results}\label{results-5}}

@@

\hypertarget{limitations-1}{%
\subsection{Limitations}\label{limitations-1}}

\hypertarget{future-development-extending-the-task-1}{%
\subsection{Future development / extending the task}\label{future-development-extending-the-task-1}}

\hypertarget{conclusion-1}{%
\section{Conclusion}\label{conclusion-1}}

>>>>

@@

\begin{itemize}
\tightlist
\item
  individual differences in developmental psychology:
\item
  reliable tasks, variation needed, more trials
\item
  existing tasks for social cognition: wellman
\item
  goal of the current project: standardized, easy to use continuous methods
\end{itemize}

@@

\begin{itemize}
\tightlist
\item
  face value of task (or maybe in intro already?)
\end{itemize}

@@

\hypertarget{data-processing}{%
\subsection{Data processing}\label{data-processing}}

@@

\hypertarget{procedure}{%
\subsection{Procedure}\label{procedure}}

@@

\hypertarget{results}{%
\subsection{Results}\label{results}}

@@

We captured a developmental trajectory of gaze cue understanding: with increasing age, participants get more and more accurate in their performance. In the hedge version, children's click imprecision drops with age, while in the box version the proportion of correct responses increases (see Figure 2 A and F). By the end of their sixth year of life, children come close to the adult's proficiency level. We find interindividual variation across studyversions and age groups: some three-year-olds are more accurate in their responses than some five-year-olds.

@@

As Figure 2 A and F show, our remotely collected data closely resembled the data from the kindergarten sample. We found a minor difference in that children that participate remotely are slightly more precise. This difference was mainly driven by the younger participants and especially prominent in the box version of the task. It is conceivable that caregivers were especially prone to help with the behavior of younger children. In the box version, caregivers might have had more opportunities to interfere since they carried out the clicking for their children.

\hypertarget{discussion}{%
\subsection{Discussion}\label{discussion}}

Study 1 showed that our newly implemented balloon finding task can be used to study gaze cue understanding in both children and adults. With increasing age, participants got more and more precise in locating the target. We found inter-individual variation in across all age groups. Furthermore, we found a comparable developmental trajectory for an unsupervised remote child sample. This underlines how flexibly our new task can be used.

@@

Based on the results of Study 1, we wanted to further investigate whether the variation that we captured with our balloon finding task is reliable. For this aim, we assessed the internal consistency and test-retest reliability. The pre-registrations can be found here: \url{https://osf.io/xqm73} (child sample) and here: \url{https://osf.io/nu62m} (adult sample). Participants were equally distributed across the two study versions. The study was approved by an internal ethics committee at the Max Planck Institute for Evolutionary Anthropology. Data was collected between XXX 2021 and XXX 2022.

@@

\hypertarget{results-1}{%
\subsection{Results}\label{results-1}}

@@

For estimating the internal consistency, we analyzed the raw performance per subject of the first test day.
Our main analysis focuses on an odd-even split on our data.\\
In the hedge version, odd-even splitting yielded an estimate of 0.86 for the child sample (see Figure 2B), and an estimate of 0.77 for the adult sample (see Figure 2C).
In the box version, odd-even splitting yielded an estimate of 0.55 for the child sample (see Figure 2G), and an estimate of 0.76 for the adult sample (see Figure 2H).

A recent paper by {[}TODO: insert citation splithalfr paper{]} presents new techniques to analyze internal consistency.
The modern statistical approach of stratification allows for a better representation of the data and experimental structure.
To compare our traditional approach of a simple odd-even split, we explored the results of random, odd-even and first-second-testhalf splits without and with stratification by target position. As can be seen in Table 1, stratifying by target position leads to similar or even higher estimates.
As might be expected, we found higher coefficients for the samples with higher variation, i.e.~for our continuous hedge version of the task.

\begin{tabular}{l|l|l|l|r|r|r}
\hline
study version & age group & splitting method & stratification & mean estimate & lower 95\%CI & upper 95\%CI\\
\hline
hedge & kids & random & none & 0.8043888 & 0.6920419 & 0.9164789\\
\hline
hedge & kids & random & target position & 0.9476184 & 0.8969928 & 0.9755679\\
\hline
hedge & kids & odd even & none & 0.8594840 & 0.7205078 & 0.9093440\\
\hline
hedge & kids & odd even & target position & 0.8024165 & 0.5332674 & 0.9298445\\
\hline
hedge & kids & first second & none & 0.8181923 & 0.6947852 & 0.9381469\\
\hline
hedge & kids & first second & target position & 0.8024165 & 0.5203456 & 0.9246955\\
\hline
hedge & adults & random & none & 0.8653142 & 0.7987080 & 0.9165413\\
\hline
hedge & adults & random & target position & 0.9239187 & 0.8751052 & 0.9518373\\
\hline
hedge & adults & odd even & none & 0.7686066 & 0.5965930 & 0.8631549\\
\hline
hedge & adults & odd even & target position & 0.8024056 & 0.6640335 & 0.8818732\\
\hline
hedge & adults & first second & none & 0.6752549 & 0.5261556 & 0.7964930\\
\hline
hedge & adults & first second & target position & 0.8024056 & 0.6561634 & 0.8822399\\
\hline
box & kids & random & none & 0.7660606 & 0.5458261 & 0.8598990\\
\hline
box & kids & random & target position & 0.9088431 & 0.8521932 & 0.9424099\\
\hline
box & kids & odd even & none & 0.5483231 & 0.3375113 & 0.6922869\\
\hline
box & kids & odd even & target position & 0.6137607 & 0.3960722 & 0.7393150\\
\hline
box & kids & first second & none & 0.5022750 & 0.2369860 & 0.6633424\\
\hline
box & kids & first second & target position & 0.6137607 & 0.3772301 & 0.7354956\\
\hline
box & adults & random & none & 0.8004204 & 0.6814629 & 0.8755589\\
\hline
box & adults & random & target position & 0.8657569 & 0.7669845 & 0.9221076\\
\hline
box & adults & odd even & none & 0.7597443 & 0.6424789 & 0.8387192\\
\hline
box & adults & odd even & target position & 0.6673433 & 0.4851349 & 0.7846746\\
\hline
box & adults & first second & none & 0.6685946 & 0.4850376 & 0.7642744\\
\hline
box & adults & first second & target position & 0.6673433 & 0.4845532 & 0.7820390\\
\hline
\end{tabular}

Our results indicated that the measured variation was systematic. These results hold for both the continuous hedge version as well as the discrete box version of the task.

@@

@@

\hypertarget{results-2}{%
\subsection{Results}\label{results-2}}

@@

\hypertarget{limitations}{%
\subsection{Limitations}\label{limitations}}

\hypertarget{future-development-extending-the-task}{%
\subsection{Future development / extending the task}\label{future-development-extending-the-task}}

\hypertarget{conclusion}{%
\section{Conclusion}\label{conclusion}}
